---
title: "Week 4 assignment"
author: "Mathilde"
date: "24/3/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Week 4 assignment

# Data
```{r}
#set working directory
setwd("H:/Forskningsår/Coursera/Week 4 assignment")


#URL
zip <-  "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"

download.file(zip, "Dataset.zip")

#unzip
unzip("Dataset.zip") #hvad går galt?

list.files("H:/Forskningsår/Coursera/Week 4 assignment/UCI HAR Dataset")

#Getting all dataframes from the dataset
features <- read.table("UCI HAR Dataset/features.txt", col.names = c("n","functions"))
activities <- read.table("UCI HAR Dataset/activity_labels.txt", col.names = c("code", "activity"))

#test
subject_test <- read.table("UCI HAR Dataset/test/subject_test.txt", col.names = "subject")
x_test <- read.table("UCI HAR Dataset/test/X_test.txt", col.names = features$functions)
y_test <- read.table("UCI HAR Dataset/test/y_test.txt", col.names = "code")

#train
subject_train <- read.table("UCI HAR Dataset/train/subject_train.txt", col.names = "subject")
x_train <- read.table("UCI HAR Dataset/train/X_train.txt", col.names = features$functions)
y_train <- read.table("UCI HAR Dataset/train/y_train.txt", col.names = "code")


```

# 1. Merges the training and the test sets to create one data set.

```{r}

#Merging the train and test data
X <- rbind(x_train, x_test)
Y <- rbind(y_train, y_test)
Subject <- rbind(subject_train, subject_test)
Merged_Data <- cbind(Subject, Y, X)

```


# 2. Extracts only the measurements on the mean and standard deviation for each measurement. 

```{r}
library(dplyr)

#merger data
TidyData <- Merged_Data %>% select(subject, code, contains("mean"), contains("std"))

```


# 3. Uses descriptive activity names to name the activities in the data set

```{r}

TidyData$code <- activities[TidyData$code, 2]

```


# 4. Appropriately labels the data set with descriptive variable names. 

```{r}
#names for variables/columns
names(TidyData)[2] = "activity"
names(TidyData)<-gsub("Acc", "Accelerometer", names(TidyData))
names(TidyData)<-gsub("Gyro", "Gyroscope", names(TidyData))
names(TidyData)<-gsub("BodyBody", "Body", names(TidyData))
names(TidyData)<-gsub("Mag", "Magnitude", names(TidyData))
names(TidyData)<-gsub("^t", "Time", names(TidyData))
names(TidyData)<-gsub("^f", "Frequency", names(TidyData))
names(TidyData)<-gsub("tBody", "TimeBody", names(TidyData))
names(TidyData)<-gsub("-mean()", "Mean", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-std()", "STD", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-freq()", "Frequency", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("angle", "Angle", names(TidyData))
names(TidyData)<-gsub("gravity", "Gravity", names(TidyData))

```


# 5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r}
#making a final study population
FinalData <- TidyData %>%
    group_by(subject, activity) %>%
    summarise_all(funs(mean))
write.table(FinalData, "FinalData.txt", row.name=FALSE)


```

